\documentclass{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage[table,xcdraw]{xcolor}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{tabularx}
\usepackage{setspace} 



\usepackage{enumitem}
\setlist[itemize]{noitemsep, nolistsep}
\setlength\lineskip{1pt}
\renewcommand\baselinestretch{0}
\setlength\parindent{1pt}
\setlength\intextsep{1pt}




%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
%  ididit    \titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
%\titlespacing{\section}{0pt}{3pt}{3pt}
% ididit  \titlespacing*{\section}{0mm}{1.75mm}{0mm}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
%   ididit   \hyphenation{im-pre-se}

%SHIKHERS

\usepackage{wrapfig}
\usepackage{array}
\usepackage{titlesec}
\usepackage{hyperref}
\pagenumbering{gobble}
\titlespacing*{\section}{0mm}{1.75mm}{0mm}



%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}
\usepackage{geometry}
\geometry{a4paper, portrait, margin=1.5cm}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge AMAN UPADHYAY \textsc{}
	}\lineskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data


\begin{center}

     {\footnotesize Fourth Year Dual Degree, Department of Biological Sciences and Bioengineering, Indian Institute of Technology (IIT), Kanpur} \\
    
     {\footnotesize amanup@iitk.ac.in   |   aman161upadhyay@gmail.com 

\end{center}


%Section: Education
\section*{Educational Qualifications}
% Please add the following required packages to your document preamble:
% 
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}


\centering
\begin{tabular}{rl}	
 \textsc{July} 2014-Present & M.Tech. in \textsc{Biological Sciences and Bioengineering} | B.S. in \textsc{Chemistry} (Dual) \\ &\textbf{Indian Institute of Technology}, Kanpur\\

&\normalsize \textbf{CPI: 8.63/10}\\&\\ 

\vspace{0.5mm}

\textsc{April} 2012 – \textsc{March} 2013& Higher Secondary Certificate Examination (12th GRADE) [MSBSHSE] \\ 
&\normalsize \textbf{Percentage: 79.7\%}\\&\\
\vspace{0.5mm}
\textsc{April} 2010 – \textsc{March} 2011 & Senior  Secondary Certificate Examination (10th GRADE) [MSBSHSE] \\ 
&\textbf{Percentage: 92.2\%}

\end{tabular}

\vspace{-3mm}

%Section: Scholarships and additional info
\section*{ \begin{flushleft} Scholastic Achievements \end{flushleft}  }

\vspace{-2mm}

\begin{itemize}
    \item Secured \textbf{All India Rank 4142} in JEE ADVANCED 2014 among \textbf{150,000} candidates.
    \item Semester Performance Index \textbf{(S.P.I) 10/10} in 4th and 7th semesters among 1100+ students.
    \item Recipient of \textbf{INSPIRE Fellowship} by DST to students inclined to pursue a career in scientific research.
    \item Secured \textbf{99.25} percentile in JEE MAINS 2014 among \textbf{1,400,000} candidates.
    \item Secured rank \textbf{25} (\textbf{99.975} percentile) in Maharashtra Talent Search Exam 2010 among \textbf{100,000} candidates.
    \item Secured \textbf{All India Rank 1179} in National Science Olympiad 2009 organized by Science Olympiad Fndn.
\end{itemize}

\vspace{-3mm}


\section*{ \begin{flushleft} Research Projects \end{flushleft} }

\vspace{-3mm}

\begin{itemize}

\item \textbf{Investigating the presence of selenium hydrogen bonds in proteins}
     \hfill\textit{July 2017 - Present}
     \\[0pt]  \textit{\small	 Advisor: Prof. R. Sankararamakrishnan, Dept. of Biological Sciences and Bioengineering, IIT Kanpur}  
    \begin{itemize}
        \item Studied huge amounts of data from PDB to investigate unknown noncovalent interactions.    
        \item Studied the pattern of occupancy factors and correlated it to the stability of a particular protein. 
        \item Investigating the presence of selenium hydrogen bonds in proteins using protein visualization tools and Quantum Mechanical calculations.
        
        \vspace{-1mm}
    \end{itemize}
    \vspace{1.5mm}
     \item \textbf{Luminescent Lanthanide Nanoparticles for Bioimaging Applications}
     \vspace{-1mm}
     \hfill\textit{July 2016 - April 2017}
     \\[3pt]  \textit{\small Advisor: Prof. A.K. Patra, Dept. of Chemistry, IIT Kanpur } 
    \begin{itemize}
        \item Studied several reaction schemes and prepared organic ligands having thiol and amino groups.
        \item Synthesized and studied thiophilic gold nanoparticles 
        \item Attached ligands to gold nanoparticles which were attached to certain therapeutic drug.
        \item Studied the diagnostic bioimaging applications of the lanthanide complexes synthesized.
    \end{itemize}
    
\end{itemize}
\vspace{-1mm}
\vspace{-2mm}
%Section: Languages
\section*{ \begin{flushleft} Selected Projects and Term Papers \end{flushleft}  }

\vspace{-3mm}

\begin{itemize}

\item \textbf{Application of electroceuticals to the treatment of optic neuritis}
     \hfill\textit{August-November 2017}
     
     \vspace{-1mm}
     
     \\[3pt] \textit{\small Advisor: Prof. D.S. Katti, Dept. of Biological Sciences and Bioengineering, IIT Kanpur  }  
    \begin{itemize}
        \item Designed a cure for optic neuritis (a condition in Multiple Sclerosis) by replacing the damaged optic nerves by an electroceutical device which works as an artificial neuron. 
        \item Received an A grade for the innovative ideation, insights, research, term paper and presentation. 
    \end{itemize}
    
  
    
    \item \textbf{Normalization of Religious Ethics}
     \hfill\textit{January-April 2017}
     \vspace{-1mm}
     
     \\[3pt]  \textit{\small Advisor: Prof. Vineet Sahu, Dept. of Philosophy HSS,
     IIT Kanpur  }
    \begin{itemize}
        \item Awarded an A grade for researching religious practices', studying their moral implications and their relevance in today's world; suggested a possibly better morality model based on Ayn Rand's work. 
    \end{itemize}
    
    \item \textbf{The How’s and Why’s of The Great Economic Depression, 1929}   \hfill\textit{May-July 2015} \\
    
    \vspace{-1mm}
    
    \\[3pt] \textit{\small Business Club, IIT Kanpur }
    \begin{itemize}
        \item Researched the complications associated with the Classical and the Keynesian Macroeconomics.
        \item Made inferences as to how such recession and depression periods can be avoided in future. 
    \end{itemize}
    
\vspace{-3mm}


\end{itemize}
\section*{\begin{flushleft} Technical skills \end{flushleft}  }
\begin{itemize}
    
    \vspace{-2mm}
    
    \item  Programming Languages- Proficient: C | Python | R  | MATLAB | Basic : Bash | Ruby | C++ | FORTRAN | HTML 
     \item Softwares- PyMol |  Gaussian | ChemBiodraw | MS Office | LATEX | Adobe Photoshop | GitHub
\end{itemize}

\vspace{-3mm}

\section*{\begin{flushleft} Relevant Courses \end{flushleft}  } 

\vspace{-2mm}

\begin{tabular}{lll}
 Bioinformatics  &  Quantum Chemistry Computation  & Machine Learning \\
 Biological Systems  &  Computer Programming for Chemistry  &  Biotechnology       \\
  Quantum Mechanics  &  Probability and Statistics &  Statistical Mechanics         \\
     \\
\end{tabular}

\vspace{-1mm}
 
\begin{itemize}
    \item  Courses related to Biochemistry, Neurobiology, Numerical Methods, Programming and Algorithms, Real Analysis, Vector Calculus, Linear Algebra, Differential Equations, Material Science.
\end{itemize}



\end{document}