\documentclass{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage[table,xcdraw]{xcolor}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{tabularx}
\usepackage{setspace} 



\usepackage{enumitem}
\setlist[itemize]{noitemsep, nolistsep}
\setlength\lineskip{2pt}
\renewcommand\baselinestretch{0}
\setlength\parindent{2pt}
\setlength\intextsep{2pt}




%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
%  ididit    \titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
%\titlespacing{\section}{0pt}{3pt}{3pt}
% ididit  \titlespacing*{\section}{0mm}{1.75mm}{0mm}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
%   ididit   \hyphenation{im-pre-se}

%SHIKHERS

\usepackage{wrapfig}
\usepackage{array}
\usepackage{titlesec}
\usepackage{hyperref}
\pagenumbering{gobble}
\titlespacing*{\section}{0mm}{1.75mm}{0mm}



%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}
\usepackage{geometry}
\geometry{a4paper, portrait, margin=1.5cm}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge AMAN UPADHYAY \textsc{}
	}\lineskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data


\begin{center}

     {\footnotesize Fourth Year Dual Degree, Department of Biological Sciences and Bioengineering, Indian Institute of Technology (IIT), Kanpur} \\
    
     {\footnotesize amanup@iitk.ac.in   |   aman161upadhyay@gmail.com 

\end{center}


%Section: Education
\section*{Educational Qualifications}
% Please add the following required packages to your document preamble:
% 
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}


\centering
\begin{tabular}{rl}	
 \textsc{July} 2014-Present & M.Tech. in \textsc{Biological Sciences and Bioengineering} | B.S. in \textsc{Chemistry} (Dual) \\ &\textbf{Indian Institute of Technology}, Kanpur\\

&\normalsize \href{https://github.com/aman161upadhyay/CV/blob/master/CPI%20Transcript.pdf}{\textbf{CPI: 8.63/10}}\\&\\ 

\vspace{0.5mm}

\textsc{April} 2012 – \textsc{March} 2013& Higher Secondary Certificate Examination (12th GRADE) [MSBSHSE] \\ 
&\normalsize \textbf{Percentage: 79.7\%}\\&\\
\vspace{0.5mm}
\textsc{April} 2010 – \textsc{March} 2011 & Senior  Secondary Certificate Examination (10th GRADE) [MSBSHSE] \\ 
&\textbf{Percentage: 92.2\%}

\end{tabular}

\vspace{-1.5mm}

%Section: Scholarships and additional info
\section*{ \begin{flushleft} Scholastic Achievements \end{flushleft}  }

\vspace{-3mm}

\begin{itemize}
    \item \textbf{All India Rank 4142} in JEE ADVANCED 2014 among \textbf{150,000} candidates.
    \item Semester Performance Index \textbf{(S.P.I) 10/10} in 4th and 7th semesters among 1100+ students.
    \item Recipient of \href{http://dst.gov.in/innovation-science-pursuit-inspired-research-programme}{\textbf{INSPIRE Fellowship}} awarded by DST to students inclined to pursue a career in scientific research.
    \item \textbf{99.25} percentile in JEE MAINS 2014 among \textbf{1,400,000} candidates.
    \item \textbf{Rank 25} (\textbf{99.975} percentile) in Maharashtra Talent Search Exam 2010 among \textbf{100,000} candidates.
    \item \textbf{All India Rank 1179} in National Science Olympiad 2009 organized by Science Olympiad Foundation
\end{itemize}

\vspace{-1.5mm}


\section*{ \begin{flushleft} Research Projects \end{flushleft} }

\vspace{-4mm}

\begin{itemize}

\item \textbf{Investigating the presence of selenium hydrogen bonds in proteins}
     \hfill\textit{July 2017 - Present}
     \\[0pt]  \textit{\small	 Advisor: \href{http://home.iitk.ac.in/~rsankar/}{Prof. R. Sankararamakrishnan}, Dept. of Biological Sciences and Bioengineering, IIT Kanpur}  
    \begin{itemize}
        \item Analyzed \textbf{huge} amounts of \textbf{Protein Data} (PDB) to investigate unknown noncovalent interactions.    
        \item Studied the pattern of occupancy factors and correlated it to the stability of a particular protein. 
        \item \textbf{Investigating the presence of selenium hydrogen bonds} in proteins using protein visualization tools and Quantum Mechanical calculations.
        
        \vspace{-1mm}
    \end{itemize}
    \vspace{1.5mm}
     \item \textbf{Luminescent Lanthanide Nanoparticles for Bioimaging Applications}
     \vspace{-1mm}
     \hfill\textit{July 2016 - April 2017}
     \\[3pt]  \textit{\small Advisor: \href{https://sites.google.com/site/ashiskpatra/} {Prof. A.K. Patra}, Dept. of Chemistry, IIT Kanpur } 
    \begin{itemize}
        \item Synthesized a lanthanide complex linked with organic ligands having thiol and amino groups.
        \item \textbf{Synthesized} and studied thiophilic \textbf{gold nanoparticles} to which the Ln(ligands) were covalently bonded.
        \item The nanoparticle-lanthanide complex couple acted as a \textbf{therapeutic and diagnostic(theranostic) drug}.  
     \item \textbf{Tested successfully} the \textbf{diagnostic bioimaging applications} of the theranostic drug synthesized.
    \end{itemize}
    
\end{itemize}

\vspace{-2mm}


\begin{itemize}

\item \textbf{Application of electroceuticals to cure optic neuritis}
     \hfill\textit{August-November 2017}
     
     \vspace{-1mm}
     
     \\[3pt] \textit{\small Advisor: \href{https://www.iitk.ac.in/new/dhirendra-s-katti}{Prof. D.S. Katti}, Dept. of Biological Sciences and Bioengineering, IIT Kanpur  }  
    \begin{itemize}
        \item \textbf{Designed} a cure for optic neuritis (a condition in Multiple Sclerosis) by replacing the damaged optic nerves by an \textbf{electroceutical} device which works as an \textbf{artificial neuron}. 
        \item Received an \textbf{A grade for the innovative ideation}, insights, research, \href{https://github.com/aman161upadhyay/Projects-Term-Papers/blob/master/Biomaterial_Term%20Paper_OpticNeuritis.pdf}{ term paper} and presentation. 
    \end{itemize}
    
  
    
    \item \textbf{Normalization of Religious Ethics}
     \hfill\textit{January-April 2017}
     \vspace{-1mm}
     
     \\[3pt]  \textit{\small Advisor: \href{http://home.iitk.ac.in/~vineet/}{Prof. Vineet Sahu}, Dept. of Philosophy HSS,
     IIT Kanpur  }
    \begin{itemize}
        \item Awarded an \textbf{A grade} for researching religious practices', studying their moral implications and their relevance in today's world.
        \item Suggested a possibly \textbf{better morality model} based on Ayn Rand's work. 
    \end{itemize}
    
    \item \textbf{The How’s and Why’s of The Great Economic Depression, 1929}   \hfill\textit{May-July 2015} \\
    
    \vspace{-1mm}
    
    \\[3pt] \textit{\small \href{http://students.iitk.ac.in/bclub/}{Business Club}, IIT Kanpur }
    \begin{itemize}
        \item Researched the complications associated with the Classical and the Keynesian \textbf{Macroeconomics}.
        \item Made \textbf{insights} and inferences as to how such \textbf{recession} and \textbf{depression} periods can be avoided in future. 
    \end{itemize}
    
\vspace{-1.5mm}


\end{itemize}
\section*{\begin{flushleft} Technical skills \end{flushleft}  }
\begin{itemize}
    
    \vspace{-3mm}
    
    \item  Programming Languages: C | C++ | Python | R  | MATLAB | Bash | Ruby  | FORTRAN | HTML | SQL 
     \item Softwares/Platforms: MS Excel | LATEX | Adobe Photoshop | GitHub | PyMol |  Gaussian | MS Powerpoint | MS Word
\end{itemize}

\vspace{-1.5mm}

\section*{\begin{flushleft} Relevant Courses \end{flushleft}  } 

\vspace{-3mm}

\begin{tabular}{lll}
 Bioinformatics  &  Quantum Chemistry Computation  & Machine Learning \\
 Numerical Methods  &  Computer Programming for Chemistry  &  Programming and Algorithms       \\
  Biological Systems  &  Quantum Mechanics  &  Biotechnology       \\
  Linear Algebra &  Probability and Statistics   &   Vector Calculus     \\
     \\
\end{tabular}

\vspace{-1mm}
 
\begin{itemize}
    \item  \textbf{Courses related to} Biochemistry, Neurobiology, Real Analysis, Differential Equations, Material Science, Statistical Mechanics  .
\end{itemize}



\end{document}
